\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-19 tex/paper.tex
Added more run-time explanations

\par \textbf{POST entity} \\
Creating a new entity in the system is a constant time operation for containers and content as they
only have to be inserted as new documents in MongoDB, which is a O(1)
operation~\cite{MONGOPERFOMANCE}. Even though the insertion itself has constant run-time the index 
needs to be updated or some times even rebuilt, which can slow the time before the document is
accessible in constant time. When inserting files they need to be chunked in to pieces and inserted
into GridFS, this results in n/s insertions where n is the size of the file and s is the chunk size. 
The insertion of files can then be regarded as O(n) if the size of the file is regarded, but if n is
regarded as the number of files in the system the upper bound is constant as the insertion for files
is made in the same way as for other documents.

>>>>

\par \textbf{POST/Create entity} \\
Creating a new entity in the system is a constant time operation for containers and content as they
only have to be inserted as new documents in MongoDB, which is a O(1)
operation~\cite{MONGOPERFOMANCE}. Even though the insertion itself has constant run-time the index
needs to be updated or some times even rebuilt, which can slow the time before the document is
accessible in constant time. When inserting files they need to be chunked in to pieces and inserted
into GridFS, this results in n/s insertions where n is the size of the file and s is the chunk size.
The insertion of files can then be regarded as O(n) if the size of the file is regarded, but if n is
regarded as the number of files in the system the upper bound is constant as the insertion for files
is made in the same way as for other documents.\\

\par \textbf{Snapshot creation} \\
In the creation of a snapshot all meta data in the tree that the snapshot is taken of is duplicated,
meanwhile the files remain the same, this results in n insertions where n is the number of
containers and content entities in the subtree. A snapshot insertions runtime is therefore
$\theta(n)$ and O(n). \\

\par \textbf{Delete entity} \\
Deleting an entity is a constant time operation when that entity does not have any children. When
the entity has children all those children has to be deleted too which will be done in the same
manner as the project tree is built and therefore results in the same runtime, O(n) as an upper
bound, where n is the number of entities in the subtree.

\par \textbf{PUT/Update entity} \\
The update operation in MongoDB completely replaces a document with another in regards to their
unique identifier. This could be seen as a deletion of the old document and an insertion of the new
document, but with the same id, which makes it unnecessary to update the index for the unique id
(other indices might have to be updated though). As both deletion and insertion are constant time
operations, update is also O(1).\\
